Live and Let Die? (Delayed Issues not Harder to Resolve)

### 2015-08-18 lucas.tex
Changed mean/median to median/mode for survey responses and resorted the table according to these values. Close #23

\begin{tabular}{l|c|c|c|c|c}
 &  & \multicolumn{2}{c|}{agreement} & \multicolumn{2}{c}{applicability} \\\cline{1-1} 
Practitioner survey  & N & w & $\bar{x}$ & $\tilde{x}$ \\
\hline 
\textbf{Rqts errors are most expensive...} & 16 & 4.6 & 5 & 4.2 & 4 \\ 
Process maturity improves output & 17 & 4.4 & 4 & 3.9 & 4 \\ 
Most time is spent removing errors & 16 & 4.1 & 4 & 3.9 & 4 \\ 
Missing reqts are hardest to fix & 17 & 4.1 & 4 & 4.0 & 4 \\
Reuse increases prod. and qual. & 16 & 3.9 & 4 & 3.8 & 4 \\
OO-programming reduces errors & 13 & 3.9 & 4 & 3.5 & 4 \\
80-20 rule (defects to modules) & 12 & 3.8 & 4 & 4.0 & 4 \\
Adding manpower to a late project & 15 & 3.7 & 4 & 3.7 & 4 \\
Inspections can remove 90\% of defects & 18 & 3.3 & 4 & 3.5 & 4 \\
Smaller changes have higher error density & 14 & 2.8 & 3 & 3.4 & 3.5 \\
A developer is unsuited to test own code & 17 & 2.6 & 3 & 3.5 & 4\\\hline

Researcher survey \\\hline 
Process maturity improves output & 4 & 4.0 & 4 & 4.0 & 4 \\
\textbf{Rqts errors are most expensive...} & 30 & 3.8 & 4 & 3.8 & 4   \\ 
80-20 rule (defects to modules) & 6 & 3.7 & 4 & 3.5 & 4 \\
\textbf{DelayedIssueEffect} & 30 & 3.6 & 4 & -- & --  \\ 
Missing reqts are hardest to fix & 7 & 3.6 & 4 & 3.7 & 4 \\
Adding manpower to a late project & 4 & 3.5 & 4 & 3.5 & 4 \\
Inspections can remove 90\% of defects & 7 & 3.4 & 4 & 3.6 & 3 \\
Reuse increases prod. and qual. & 6 & 3.3 & 4 & 3.0 & 4 \\
OO-programming reduces errors & 6 & 3.2 & 4 & 2.7 & 3 \\
Most time is spent removing errors & 6 & 2.8 & 3 & 3.2 & 4 \\ 
Smaller changes have higher error density & 4 & 2.8 & 3 & 4.0 & 4 \\
A developer is unsuited to test own code & 7 & 2.1 & 2 & 2.4 & 3
\end{tabular}

>>>>

\begin{tabular}{l|c|c|c|c|c}
 &  & \multicolumn{2}{c|}{agreement} & \multicolumn{2}{c}{applicability} \\\cline{1-1} 
Practitioner survey  & N & med & mode & med & mode \\
\hline 
\textbf{Rqts errors are most expensive...} & 16 & 5 & 5 & 4 & 5 \\ 
Inspections can remove 90\% of defects & 18 & 4 & 5 & 4 & 5 \\
80-20 rule (defects to modules) & 12 & 4 & 5 & 4 & 5 \\
Most time is spent removing errors & 16 & 4 & 4 & 4 & 5 \\ 
Process maturity improves output & 17 & 4 & 4 & 4 & 4 \\ 
Missing reqts are hardest to fix & 17 & 4 & 4 & 4 & 4 \\
Reuse increases prod. and qual. & 16 & 4 & 4 & 4 & 4 \\
OO-programming reduces errors & 13 & 4 & 4 & 4 & 3 \\
Adding manpower to a late project & 15 & 4 & 4 & 4 & 4 \\
Smaller changes have higher error density & 14 & 3 & 3 & 3.5 & 5 \\
A developer is unsuited to test own code & 17 & 3 & 1 & 4 & 5\\\hline

Researcher survey \\\hline 
Process maturity improves output & 4 & 4 & 4 & 4 & 5 \\
\textbf{Rqts errors are most expensive...} & 30 & 4 & 4 & 4 & 4   \\ 
\textbf{DelayedIssueEffect} & 30 & 4 & 4 & -- & --  \\
Reuse increases prod. and qual. & 6 & 4 & 4 & 4 & 4 \\
80-20 rule (defects to modules) & 6 & 4 & 4 & 4 & 3 \\
Missing reqts are hardest to fix & 7 & 4 & 4 & 4 & 3 \\
OO-programming reduces errors & 6 & 4 & 4 & 3 & 4 \\
Inspections can remove 90\% of defects & 7 & 4 & 4 & 3 & 3 \\
Adding manpower to a late project & 4 & 3 & 4 & 4 & 3 \\
Most time is spent removing errors & 6 & 3 & 3 & 4 & 4 \\ 
Smaller changes have higher error density & 4 & 3 & -- & 4 & 4 \\
A developer is unsuited to test own code & 7 & 2 & 1 & 3 & 3
\end{tabular}
